Hierarchical time series forecasting in Emergency Medical Services

### 2022-11-16 manuscript/main.qmd
Added colorblind palette and theme to setup

bibliography: bibliography.bib
execute:
  echo: false
  message: false
  warning: false
  cache: true
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Annals of Emergency Medicine
      formatting: preprint
      model: 3p
      cite-style: authoryear
---

```{r}
#| label: setup
#| include: false
library(fpp3)
library(knitr)
library(kableExtra)
library(ggthemes)
library(patchwork)
#library(ggraph)
#library(igraph)
```

>>>>

bibliography: bibliography.bib
execute:
  echo: false
  message: false
  warning: false
pdf-engine: latexmk
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Annals of Emergency Medicine
      formatting: preprint
      model: 3p
      cite-style: authoryear
---

```{r}
#| label: setup
#| include: false
library(fpp3)
library(knitr)
library(kableExtra)
library(ggthemes)
library(patchwork)
# Color blind color palettes
options(
  ggplot2.discrete.colour = c("#D55E00", "#0072B2","#009E73", "#CC79A7", "#E69F00", "#56B4E9", "#F0E442"),
  ggplot2.discrete.fill = c("#D55E00", "#0072B2","#009E73", "#CC79A7", "#E69F00", "#56B4E9", "#F0E442")
)
# Few theme
ggplot2::theme_set(ggthemes::theme_few())
```
